### 2021-07-22 doc/thesis/chapters/implementation.tex
tb stuff

\includepicture [1.0] [0]  {Block diagram of the interface between cocotb and a simulator \cite{cocotbDoc}.} {bd_cocotb_interface_simulator} {img/draw.io/bd_cocotb_interface_simulator}

@@

The implemented testbench structure, as well as some specific implementation details are explained here.

@@

A testbench is equally important in the HLS implementation, as it is for the VHDL implementation.
The HDL code for the IP is written in \cplusplus and thus the testbench is also written in this language.
The execution of the testbench is done in the Xilinx HLS software.\\

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Design for Reuse}

testbench is using Firmware code! --> enables reuse and early testing on the code, before a hardware prototype exists

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Common Testbench}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Architecture (same tb for VHDL and HLS-generated HDL)}

>>>>

%TODO: use mathematical typesetting in this diagram
\includepicture [1.0] [0]  {Block diagram of the interface between cocotb and a simulator \cite{cocotbDoc}.} {bd_cocotb_interface_simulator} {img/draw.io/bd_cocotb_interface_simulator}

@@

This section describes the HLS version of the FM radio receiver implementation.
The implemented testbench structure, as well as some specific implementation details are explained here.

@@

A testbench is equally important in the HLS implementation, as it is for the VHDL implementation.
The HDL code for the IP is written in \cplusplus\ and thus the testbench is also written in this language.
The execution of the testbench is done in the Xilinx HLS software.
A detailed explanation of how an HLS testbench works in general is given in Chapter \ref{cha:HLS}.\\

The testbench is developed in a similar manner as the VHDL testbench.
It applies input data to the DUT and generates output data of multiple signals, which need to be observed.
This output data is in turn saved to output files, which are analyzed in a subsequent step.\\

The actual implementation to write the HLS signal data to a file, is implemented as a file-writer \cplusplus\ class within the HLS design code.
These code parts are only evaluated during simulation, which is achieved by using pre-processor defines.
The following code shows an example of this file-writer class.\\

\begin{CppCode}
audio_sample_t fm_receiver( ... ) {
  ...
#ifndef __SYNTHESIS__
  static DataWriter writer("data_out_audio.txt");
  writer.write(audio);
#endif
  ...
  return audio;
}
\end{CppCode}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Design For Reuse}

The testbench is especially designed around the 'Design For Reuse' segment of the SIMILAR concept, which is introduced in Section \ref{sec:SimilarProcess}.

testbench is using Firmware code to load the data! --> enables reuse and early testing on the code, before a hardware prototype exists\\

also, the same Python analyzer code is used as in the VHDL tb

@@
